Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-06-01 glsb.tex
fiddle

We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.

@@

It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.  It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.

@@

While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.

>>>>

We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.

@@

It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.  It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.  While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.

@@
